Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-01 02_Paper/paper.tex
Include confusion matrix in conclusion

Based on the prediction results presented on Table,~\subref{tab:SVM_conf_matrix , tab:MPL_conf_matrix, tab:Tree_conf_matrix}

We found the random forest performed best followed by the multilinear
perceptron and the support vector machine.

@@

By implementing ML models capable to predict the quality of the product, just by the initial conditions of the process would be a great asset for the industrial processes. Within the limits of our work, we are able to predict with 98\% certainty the product quality by implementing a supported-vector-machine with a 6-variables vector as input. 
For further work, we expect to increase the certainty of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.

>>>>

The outcome of the models shows that the random forest performed best followed by the multilinear perceptron and the support vector machine. However, by reviewing the confusion matrices presented on Table,~\ref{tab:Confusion_matrix}, multilinear perceptron would be the option of choice to be implemented at industrial applications due to the 0\% ratio in false-positive results.

@@

By implementing ML models capable to predict the quality of the product, just by the initial conditions of the process would be a great asset for the industrial processes. Within the limits of our work, we are able to predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input. 
However, our decision for industrial applications would be the MLP with 88\% accuracy as to guarantee the QC and avoid labeling a NOK piece as OK. For further work, we expect to increase the certainty of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.
